### 2016-08-16 latex/paper.tex
Total potential energy

The in-plane curvature of the rim is $\kappa_2 = 1/R$ and remains constant during flexural-torsional buckling. The out-of-plane curvature and axial twist rate are
\begin{equation}\label{eq:k2}
\kappa_2 = u'' - \frac{\phi}{R}
\end{equation}
\begin{equation}\label{eq:k3}
\kappa_3 = \phi' + \frac{1}{R} u'
\end{equation}
The symbol $()'$ indicates a derivative with respect to $s$. It can easily be verified that Equations \ref{eq:k2} and \ref{eq:k3} simplify to the standard equations for straight beams in the limit $R\rightarrow \infty$. The curvature and twist rate produce a bending moment and twisting moment equal to
\begin{equation}\label{eq:M2}
M_2 = EI_{11} \kappa_2
\end{equation}
\begin{equation}\label{eq:M3}
M_3 = GJ \kappa_3 + EI_w \kappa_3''
\end{equation}
The strain energy is decomposed into lateral bending, uniform torsion, and warping terms which are related to the curvatures.
\begin{equation}\label{eq:Urim}
U_{rim} = \frac{1}{2} EI_{22} \kappa_2^2 + \frac{1}{2} GJ \kappa_3^2 + \frac{1}{2} EI_w (\kappa_3')^2
\end{equation}

@@

\section{CONCLUSIONS}

>>>>

The in-plane curvature $\kappa_1$ is assumed to remain constant during flexural-torsional buckling. The in-plane curvature, out-of-plane curvature and twist rate are
\begin{equation}\label{eq:k1}
\kappa_1 = 1/R
\end{equation}
\begin{equation}\label{eq:k2}
\kappa_2 = u'' - \frac{\phi}{R}
\end{equation}
\begin{equation}\label{eq:k3}
\kappa_3 = \phi' + \frac{1}{R} u'
\end{equation}
The symbol $()'$ indicates a derivative with respect to $s$. It can easily be verified that Equations \ref{eq:k2} and \ref{eq:k3} simplify to the standard equations for straight beams in the limit $R\rightarrow \infty$. The curvature and twist rate produce a bending moment and twisting moment equal to
\begin{equation}\label{eq:M2}
M_2 = EI_{11} \kappa_2
\end{equation}
\begin{equation}\label{eq:M3}
M_3 = GJ \kappa_3 + EI_w \kappa_3''
\end{equation}
The total strain energy is decomposed into lateral bending, uniform torsion, and warping terms which are related to the curvatures.
\begin{equation}\label{eq:Urim}
U_{rim} = \int_0^{2\pi} \left( \frac{1}{2} EI_{22} \kappa_2^2 + \frac{1}{2} GJ \kappa_3^2 + \frac{1}{2} EI_w (\kappa_3')^2 \right)\, ds
\end{equation}
After buckling, a differential line segment $ds$ deforms to $dS$. The apparent shortening of the line segment along the $s$ direction is then
\begin{equation}\label{eq:ds}
ds - dS = ds - \sqrt{ds^2 + \left(\frac{du}{ds}ds\right)^2} \approx \frac{1}{2} (u')^2 \, ds
\end{equation}
The axial compressive force in the rim moves through this differential displacement, performing virtual work equal to
\begin{equation}\label{eq:Vrimr}
V_{rim} = \frac{1}{2} \int_0^{2\pi} N_r (u)^2 \, ds
\end{equation}

@@

\subsection{Total potential energy and buckling criterion}
The buckled shape of the wheel must be periodic, so we assume a buckled shape of the form
\begin{equation}\label{eq:modeshape}
\begin{split}
u(s) &= \delta u_n \cos{\frac{ns}{R}} \\
\phi(s) &= \delta\phi_n \cos{\frac{ns}{R}}
\end{split}
\end{equation}
The wheel becomes unstable when the increase in strain energy is exactly balanced by the virtual work for a perturbing displacement $\delta u_n, \delta\phi_n$, i.e. when
\begin{equation}\label{eq:TotPot}
U_{rim} - V_{rim} = 0
\end{equation}
Substituting the buckling mode shape Eqn. \ref{eq:modeshape} into Eqns. \ref{eq:Urim} and \ref{eq:Vrimr} and substituting into Eqn. \ref{eq:TotPot} yields the critical buckling criterion for the $n$th mode.
\begin{equation}\label{eq:Tcrit}
...
\end{equation}
\section{CONCLUSIONS}
